Joint satellite distribution of isolated galaxy pairs

### 2017-10-25 paper/paper.tex
new plots
new plot, expected number
caption

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Satellites in the MW and M31]{Local Group Satellite Distributions in
 the Illustris Simulation}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Satellites in the MW and M31]{Joint 
  satellite distribution of isolated galaxy pairs}  
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.47\textwidth]{expected_numbers.pdf}
\caption{Probability distribution for the expected number of pairs
  showing the same degree of atipicality as the Local Group. The two
  distributions correspond to different numbers of initial isolated
  pairs. On average $1\%$ of the isolated pairs should present
  satellite distributions as atypical as the Local Group.
\label{fig:expected_number}}
\end{figure}
